Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-02-28 presentation/index.qmd
binary relevance setup

- data preparation, big time-consumer is handling raw acc data
- only thigh data used. HSBC and other is only thigh data...
- all zm recording is considered as in-bed (sensor problem?)
- no sleep stages, only sleep/awake
- sensor problems during sleep, up to 20 consecutive epochs (200 sec) are treated as sleep

@@

## Circadian Proxy Features {transition="convex"}

@@

@@

@@

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.
- multiclass vs multilabel classification

>>>>

::: {.fragment}

- data preparation, big time-consumer is handling raw acc data
- only thigh data used. HSBC and other is only thigh data...
- all zm recording is considered as in-bed (sensor problem?)
- no sleep stages, only sleep/awake
- sensor problems during sleep, up to 20 consecutive epochs (200 sec) are treated as sleep
- Combine binary classifiers to produce multilabel outcomes (i.e., binary Relevance)
- Evaluated combined classifiers using weighted micro-averaging.

@@

## Circadian Proxy Features {transition="fade"}

@@

## Estimate Sleep Quality Metrics {transition="fade"}

```{r}
#| fig-asp: .4
source(here::here("presentation/code/plot_pred_example.R"))

plot_ex
```

## Estimate Sleep Quality Metrics {transition="fade"}

```{r}
#| fig-asp: .4
source(here::here("presentation/code/plot_pred_example.R"))

plot_lps
```

::: aside 
This methedology is called binary relevance.
:::

## Estimate Sleep Quality Metrics {transition="fade"}

```{r}
#| fig-asp: .4
source(here::here("presentation/code/plot_pred_example.R"))

plot_tst
```

@@

```{r}
roc_combined_plots
```

@@

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.
- multiclass vs multilabel classification
- in-bed awake/sleep is highly imbalanced -> maybe train a new classifier accounting for imbalanced data (SMOTE)
- model combined preds instead?
